Printer ballistics through texture analysis of characters

### 2013-11-28 Printer_Ballistics.tex
Experiments

%%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Printer ballistics through character's texture analysis}
\author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel\_rodrigues@aol.com}}\\
Mário Brito\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{britomar@aedu.com}}\\
Maurício Perez\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{mauriciolp84@gmail.com}}\\
Anderson Rocha\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
}

@@

\begin{table}
\label{tab:printers}
\caption{Printers used in this work}
\begin{center}
\begin{tabular}{l*{2}{c}r}
Printer           & Documents \\
\hline
Brother-HL4070CDW & 28 \\
Canon-D1150 & 28 \\
Canon-MF3240 & 28 \\
Canon-MF4370DN & 28 \\
HP-CLJ-CP2025A & 28 \\
HP-CLJ-CP2025B & 28 \\
HP-JL-CP1518 & 28 \\
Lexmark-E260D & 28 \\
OKI-C330 & 28 \\
Samsung-CLP315 & 28 \\
\end{tabular}
\end{center}
\end{table}

@@

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Discussion}
\label{sec:experiments}
%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusions}

>>>>

%%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Printer ballistics through texture analysis of characters}
\author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel\_rodrigues@aol.com}}\\
Mário Brito\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{britomar@aedu.com}}\\
Maurício Perez\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{mauriciolp84@gmail.com}}\\
Anderson Rocha\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
}

@@

\begin{table}
\label{tab:printers}
\caption{Printers used in this work}
\begin{center}
\begin{tabular}{l*{2}{c}r}
Printer           & Documents \\
\hline
Brother-HL4070CDW & 28 \\
Canon-D1150 & 28 \\
Canon-MF3240 & 28 \\
Canon-MF4370DN & 28 \\
HP-CLJ-CP2025A & 28 \\
HP-JL-CP1518 & 28 \\
Lexmark-E260D & 28 \\
OKI-C330 & 28 \\
Samsung-CLP315 & 28 \\
\end{tabular}
\end{center}
\end{table}

@@

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Discussion}
\label{sec:experiments}

As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the proprieties would be extracted. With the extracted proprieties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution. In the first instance, we needed to determine the best options for classifying the characters and attributing them to a Printer. But our final goal is not to attribute the characters to a printer, but a whole document, so in the next step, we propose a way of attributing the printer based on the classification of the characters.

\subsection{Characters Selection and Proprieties Extraction}

First we selected three characters from each one of the three sections from a document, and repeated that for all documents. There were 3x3x28 = 252 characters selected for each printer, what gave us a total of 1512.

For the proprieties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}. From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a vector of descriptors of eight values for a character. The second one gave us four per type, in other words, a sixteen sized vector.

\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{neighbor}
	\caption{Neighborhood A, leftmost, and B, rightmost, used in properties extraction (the darker pixel is the pixel-of-interest)}
\label{fig:neighbor}   
\end{center} 
\end{figure}

\subsection{Characters Classification}

The just acquired descriptors are used for evaluation the available classification algorithms. For this evaluation it was separated 66\% of the chars to be used as training (1008) and the rest for testing (504). From them we separate the most prominent and present the results in table \ref{tab:correct_classification}.

\begin{table}
\label{tab:correct_classification}
\caption{Percentage of correct classifications of printers.}
\begin{center}
\begin{small} 
\setlength{\tabcolsep}{3pt} 
\begin{tabular}{l*{5}{c}r} & \multicolumn{2}{c}{Neighborhood A} & \multicolumn{2}{c}{Neighborhood B}\\ \cline{1-5}
Method & Chars e’s & Chars t’s & Chars e’s & Chars t’s \\
\hline
Logistic & 81 & 81.3 & 85 & 84.6\\
KStar & 77.6 & 83 & 72 & 79.6\\
RotationForest & 83.1 & 85 & 81.7 & 85.7\\
NNge & 74.1 & 80.2 & 72.2 & 67.8\\
LMT & 83.8 & 84.6 & 82.7 & 85.5\\

\end{tabular}
\end{small}
\end{center}
\end{table}

Analyzing the results we can see a slightly better classification on the characters ''t'', perhaps they are more unique for each printer. The results also show that using a neighborhood of four pixels for many cases made the classification worst, what was against our intuition since its descriptors were longer than of the other neighborhood we used.

\subsection{Printer Attribution}

As said before, attributing a printer to the character is not the main objective, so it was necessary to define a logical output from the classified characters obtained in the previous step. For this purpose we choose to attribute a document to the printer that had most classified characters on it.

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusions}
